Nabi - A Preventative Solution Against JavaScript and Scriptless Tabnabbing Attacks

### 2015-05-06 paper/paper.tex
Various edits after reading through

The primary aspects of our tabnabbing prevention solution are as follows: a JavaScript permissions system, a system for whitelisting trusted domains, and a system for the detection and prevention of scriptless redirect attacks. The permissions system will dynamically allow and deny access rights of JavaScript as the user navigates tabs. This system could be implemented a number of ways, such as removing JavaScript tags from the page or changing the access rights of tab, but should inevitably strive to prevent any JavaScript execution. The whitelist provides the user with a way to maintain productivity while staying protected. The user may select trusted websites to be exempt from being blocked by the system, allowing that page to continue running JavaScript after the user has changed tabs. Lastly, the system must provide a method for handling scriptless attacks. The scriptless attack cannot detect when the user selects a different tab, so it must guess the expected time a user will spend looking at their page in order to redirect to the alternative site when they are presumably looking elsewhere. Thus the system must detect when a meta tag is used to issue a redirect request to the browser and either prevent it from doing so or informing the user that the redirect will be occurring.

\section{Results}
The current build of Nabi restricts JavaScript from running in every tab the user has switched from. The tab is then refreshed to reflect those restrictions and to the cancel the actively running JavaScript on that page. The page that is switched to is given access to run JavaScript and is also refreshed to reflect the change in permissions. This prevents JavaScript in the inactive tab from running while the user is not viewing it, but allows it to reactivate once the user returns. Because of this our strategy for defending against tabnabbing attacks allows the user to continue using the browser almost as if JavaScript has not been disabled.

>>>>

The primary aspects of our tabnabbing prevention solution are as follows: a JavaScript permissions system, a system for whitelisting trusted domains, and a system for the detection and prevention of scriptless redirect attacks. The permissions system will dynamically allow and deny access rights of JavaScript as the user navigates tabs. This system could be implemented a number of ways, such as removing JavaScript tags from the page or changing the access rights of tab, but should inevitably strive to prevent any JavaScript execution. The whitelist provides the user with a way to maintain productivity while staying protected. The user may select trusted websites to be exempt from being blocked by the system, allowing that page to continue running JavaScript after the user has changed tabs. Lastly, the system must provide a method for handling scriptless attacks. The scriptless attack cannot detect when the user selects a different tab, so it must guess the expected time a user will spend looking at their page in order to redirect to the alternative site when they are presumably looking elsewhere. Thus the system must detect when a meta tag is used to issue a redirect request to the browser and either prevent it from doing so or inform the user that the redirect will be occurring.

\section{Results}
The current build of Nabi restricts JavaScript from running in every tab the user has switched from. The tab is then refreshed to reflect those restrictions and to the cancel the actively running JavaScript on that page. The page that is switched to is given access to run JavaScript and is also refreshed to reflect the change in permissions. This prevents JavaScript in the inactive tab from running while the user is not viewing it, but allows it to reactivate once the user returns. Because of this our strategy for defending against tabnabbing attacks allows the user to continue using the browser normally without the risk of running JavaScript in a background tab.
